---
title: "Latine Politics in the U.S."
format:
    html: default
    pdf: 
      documentclass: article
      fontsize: 12pt
      colorlinks: true
      citecolor: DarkViolet
      linkcolor: DarkViolet
      urlcolor: DarkViolet
      geometry: margin=1in
      output-file: "POL330_syllabus"
---


```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tibble)
library(pander)
```

::: {.content-visible when-format="pdf"}

\begin{center}

\vspace{-5em}

\url{ {{< var course.url >}} } \vspace{-1ex}

{{< var course.time >}} {{< var course.days >}} \vspace{-1ex}

{{< var course.location >}} \vspace{-1ex}

{{< var course.semester >}}

\end{center}


## Instructor

{{< var instructor.name >}} \vspace{-1ex}

Email: [{{< var instructor.email >}}](mailto:{{< var instructor.email >}}) \vspace{-1ex}

Office: {{< var instructor.office >}} \vspace{-1ex}

Office hours: Tuesdays 1:30-3:30 pm

:::


::: {.content-visible when-format="html"}

::: {.grid .course-details .course-details-smaller}

::: {.g-col-6}
### Course details

- {{< fa calendar >}} &nbsp; {{< var course.days >}}
- {{< fa calendar-alt >}} &nbsp; {{< var course.dates >}}
- {{< fa clock >}} &nbsp; {{< var course.time >}}
- {{< fa location-dot >}} &nbsp; {{< var course.location >}}
:::

::: {.g-col-6}
### Instructor

- {{< fa user >}} &nbsp; [{{< var instructor.name >}}]({{< var instructor.url >}})
- {{< fa university >}} &nbsp; {{< var instructor.office >}}
- {{< fa envelope >}} &nbsp; [{{< var instructor.email >}}](mailto:{{< var instructor.email >}})
- {{< fa university >}} &nbsp; Office hours: Tuesdays 1:30-3:30 pm
:::

:::

# Syllabus

You can find a PDF version of the syllabus with the weekly schedule on the sidebar of this page.

:::


## Course Overview

This course will provide an overview of how Latines interact with, relate to, and find representation in the American political system. We will begin by discussing Latine identity, identifying and describing the demographics of this population, and analyzing the extent to which Latines have politicized identities. We will then analyze historical and demographic trends, including immigration patterns and policies as well as Chicano social and labor movements. After that, we will discuss Latine political behavior, where we will cover Latine public opinion, partisan affiliations, voting patterns, and representation. We will finish the course by discussing the role of Latines in recent elections and the potential for multiracial and multiethnic coalitions.


## Learning Outcomes

- Develop an understanding of the complexity of Latine identity in the United States
- Situate Latine politics in the United States in historical and sociopolitical context
- Think critically about the interactions between Latine political behavior and American political institutions
- Apply the theories and concepts from research on Latine politics to current events


## Work and Assessment

### Required Text:

- Beltrán, Cristina. 2010. *The Trouble with Unity: Latino Politics and the Creation of Identity.* New York, NY: Oxford University Press.



### Course Expectations

Students are expected to attend class and participate during class discussions. This course has both a lecture and a discussion component. The lectures will incorporate the readings assigned for that day/week. I expected you will have completed all readings prior to class and will come prepared with comments and questions. Readings can be accessed through the library resources or, when not available through the library, via Canvas.

- If you do not have a subscription to *The New York Times*, please sign up through the school here: <https://accessnyt.com/>


### Course Workload

This is a 4-credit hour course, meaning that you are expected to spend 12 hours of work each week (including the 3 hours spent in the classroom). This roughly means that you will spend about 2 hours on readings for each class period, and 3 hours each week working on the different assignments (pace yourself!).


### Assignments and grades

Final course grades will be assigned as follows:

```{r grades, include=FALSE}
grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%", "C−", "70–72%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "83–86%", "D",  "63–66%",
  "B−", "80–82%", "D−", "60–62%",
  "C+", "77–79%", "F",  "< 60%"
)
```

<div class="centered-table">

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lclc",
               col.names = c("Grade", "Range", "Grade", "Range"))
```

<div>


Final grades will be calculated based on the following components:

**Participation (20%)**: All students are expected to be active participants in class discussions. Our learning experience will be enhanced if you come prepared and ready to share your comments, insights, and/or questions from the material covered in the lectures and readings with the rest of the class.

  - <ins>*Attendance policy:*</ins> Attendance is part of your participation grade, and while there is no separate grade for attendance it is a prerequisite for in-class participation. That said, to accommodate unforeseeable circumstances, you have two *unexcused* absences that will not affect your participation grade. Please let the instructor know about any excused absences you anticipate during the semester. Note that students who are absent, whether excused or not, are still expected to submit the weekly summary corresponding to that class period.


**Weekly summaries (20%)**: Each week for seven weeks, you will summarize one article from the week's readings (the reading you can summarize has a {{< fa pen >}} after it in the course schedule). There are 10 weeks in the semester where you can write a summary, so you can skip some weeks. It is up to you to decide which weeks to skip. The summary must be no longer than three-quarters of a page (single-spaced, 12-point font) and must include the full citation of the reading at the top of the page. These summaries must be submitted via Canvas before class time on the day the reading was assigned.

**Response paper (10%)**: Students will write a response paper (2 double-spaced pages, 12-point font) where they integrate the readings for a given week. At the beginning of the semester, students will choose a week for their response paper. In the response paper, you will highlight the connections between the readings, write about their applicability to the role of Latines in American politics today, and offer a critique of the readings as a whole. You may choose to focus more on applicability to today or a critique of existing research. The response paper is due on the Friday of the chosen week.


**Campaign memo (15%)**: Students will write a campaign memo for a 2026 Senate campaign focused on a strategy for Latine outreach. Students must provide sufficient background on the political attitudes and behaviors of Latinos/as, provide clear takeaways, and propose strategies to appeal to Latine voters in their respective state. The audience for this paper is a political campaign staff.


**Research Design Paper (25% total)**: Students will propose a research design to answer a question of interest. This paper must include an introduction, a literature review that situates the present question in the broader field, an answer to the question (the argument/theory), and a proposed design to answer the question. Students should meet with the instructor to discuss the paper and think about how one might design a study to answer the question of interest. This paper will be broken down into different parts that will be due throughout the semester.


**Oral Presentation (10%)**: Students will give an oral presentation based on research design paper. This will take the form of a conference presentation.

- Papers must be submitted via Canvas. Late submissions will be penalized with one point off for each 24-hour period after the due date.



## Course Conduct

In this class, we will discuss politics *and* the people who participate (or not) in politics, and we will do so in a respectful environment. As in bound to be the case when we talk about politics, we may discuss topics that might be controversial or of a sensitive nature for some or all in our group. Our goal in this class is to have constructive discussions about the politics of Latinos in the United States. Derogatory comments toward other students will not be tolerated.


## Communication Policy

If you have questions about class in general or about a specific assignment, you can email me or come by my office. You can expect a response within 24 hours (unless you email me on Friday). Students are also more than welcome to attend office hours, as this is time set aside specifically for you. In addition, if my office door is open, feel free to stop by. Please note that I will not be "pre-grading" assignments, but I am happy to answer clarifying questions about them either via email or, preferably, during office hours.


## Regrading Policy

If a student wishes to appeal a grade, they must do so in writing within one week of receiving their graded assignment back. The student must indicate clearly what part of the assignment's grading they disagree with, making sure to respond to the instructor's comments in that section and making their case for why they should not have been deducted points. These requests should be done via email and the subject name should read "POL 330 Regrading request - [Name of assignment]." 


## Honor Code

Students are expected to do their own work and cite sources appropriately. Plagiarism will not be tolerated. In other words, students will be held to the standards of the Agnes Scott Honor System to which they agreed when enrolling at this institution. The Agnes Scott College honor code embodies an ideal of character, conduct, and citizenship, and is an important part of the College’s mission and core identity. This applies especially to academic honesty and integrity. Passing off someone else’s work (or Chat GPT's) as your own represents intellectual fraud and theft and violates the core values of our academic community. To be honorable, you should understand not only what counts as academic dishonesty, but also how to avoid engaging in these practices.


You are responsible for the content of any work submitted for this course. The use of artificial intelligence (AI) to generate a first draft of text is permitted, but you must review and revise any AI-generated text before submission. AI text generators can be useful tools but they are often prone to factual errors, incorrect or fabricated citations, and misinterpretations of abstract concepts. I neither encourage nor discourage their use, but utilize them with caution.



## Course Accessibility and Academic Accommodations

Agnes Scott College views disabilities as an integral part of the rich diversity of our community and strives to make all learning experiences as accessible as possible.  If you are a student who receives academic accommodations through the Office of Accessible Education, please schedule a meeting with me within the first two weeks of classes to discuss how your accommodations will be implemented for this course.  During this meeting, you are not expected to disclose any details concerning your disability, though you may discuss these details at your discretion.

If you are a student with a disability---physical, medical, psychological, or learning-specific---and have not connected with Accessible Education to discuss your accessibility needs, please visit the [main Office of Accessible Education webpage](https://www.agnesscott.edu/academicadvising/accessible-education/index.html) to learn more about accommodations, helpful resources and support, available through the Office of Accessible Education.  Students who register for accommodations during the semester should schedule a meeting with me after accommodations have been approved by the Office of Accessible Education.


## Wellbeing and Mental Health

The wellbeing and mental health of students is important; if you are having trouble completing your coursework, please reach out to the [Wellness Center](https://www.agnesscott.edu/wellnesscenter/index.html). Agnes Scott College provides cost-free mental health services to help you manage personal challenges that threaten your personal or academic well-being. If you believe you are experiencing unusual amounts of stress, sadness, or anxiety, please contact the Wellness Center and ask about their [Counseling and Psychological Services](https://www.agnesscott.edu/wellnesscenter/counseling/index.html).


## Title IX

Agnes Scott is here to help you if you have experienced any form of sexual harassment or violence, dating or domestic violence, or stalking. Please talk to any faculty or staff member with whom you feel comfortable. Faculty and staff members want to support you and have been trained to help. They will also inform the Title IX office so that you learn about options available to you. If you do not want college administrators to know what you have experienced, you may talk to the chaplain, as well as nurses or counselors in the Wellness Center with complete confidentiality. They will not tell anyone what you share with them unless you give your express permission. You may contact the Title IX Coordinator directly at <T9Coordinator@agnesscott.edu>.


## Diversity and Inclusion

Agnes Scott is a diverse and inclusive community. As one of the most diverse colleges in the nation, ASC is ideally positioned to be the model of a diverse and inclusive community that society can aspire to be. Such diversity raises the intellectual quality of the classroom experience, creating a unique environment for learning to understand and navigate the challenges of our times. By studying, living, and playing together, Agnes Scott College’s remarkably diverse student body hones the habits of mind, skills, and knowledge essential to ethical and innovative leadership in our increasingly heterogeneous and global society.  As such, this course adheres to the principles of diversity and inclusion as integral to the Agnes Scott community and respects people from all backgrounds. As a first step, this course affirms people’s decisions about gender expression and identity and will use each other’s preferred names and gender pronouns at all times.



## Center for Writing and Speaking

The Center for Writing and Speaking offers one-on-one appointments with trained peer tutors who can help you improve your written and oral communication skills. You are encouraged to use this resource when working on your class assignments to make your arguments more compelling, your sentences clearer, and persistent grammatical errors nonexistent. You can schedule an appointment at <https://www.agnesscott.edu/center-for-writing-and-speaking/index.html>.


## Syllabus Change Policy

This syllabus is only a guide for the course and is subject to change with advanced notice.


::: {.content-visible when-format="pdf"}
  
## Schedule

{{< include content/01-week1.qmd >}}

{{< include content/02-week2.qmd >}}

{{< include content/03-week3.qmd >}}

{{< include content/04-week4.qmd >}}

{{< include content/05-week5.qmd >}}

{{< include content/06-week6.qmd >}}

{{< include content/07-week7.qmd >}}

{{< include content/08-week8.qmd >}}

{{< include content/09-week9.qmd >}}

{{< include content/10-week10.qmd >}}

{{< include content/11-week11.qmd >}}

{{< include content/12-week12.qmd >}}

{{< include content/13-week13.qmd >}}

{{< include content/14-week14.qmd >}}

{{< include content/15-week15.qmd >}}

{{< include content/16-week16.qmd >}}

{{< include content/17-week17.qmd >}}

{{< include content/18-week18.qmd >}}

:::

{{< include index_title.qmd >}}

